% cv_content.tex
% Content of the CV

% Aesthetics
\usepackage{xspace}
\def\epfl{\'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne\xspace}
\def\myast{\text{\,*}}

% Start
\begin{document}
\header{albert}{puig}
       {high energy physicist}

\begin{aside}
  \section{about}
    Albert Puig Navarro\\
    Born on 26-07-1984\\
    Spanish\\
    ~\\
    Avenue Chailly 22\\
    1012 Lausanne\\
    Switzerland\\
    ~\\
    \href{mailto:albert.puig@epfl.ch}{albert.puig@epfl.ch}\\
    \href{https://github.com/apuignav}{github://apuignav}\\
    %+41 (0)216939808
  %\section{languages}
    %bilingual french/english
    %spanish \& italian notions
\ifthenelse{\boolean{includeprogramming}}
{  \section{programming}
    Python, C++,\\
    Fortran, PVSS,\\
    MySQL, VB.NET\\
}{}
    \section{interests}
    high-energy physics\\
    $B$ physics\\
    radiative $B$ decays\\
    trigger techniques\\
    data analysis\\
    computing\\

    \section{last update}
    \today

\end{aside}

\section{education \& employment}

  \cventry
    {since 2012}
    {Postdoctoral Fellowship}
    {\epfl(Switzerland)}
    {}
  \cventry
    {2007--2012}
    {PhD in Physics}
    {Universitat de Barcelona (Spain)}
    {\emph{First measurements of radiative $B$ decays in LHCb}, supervised by Ricardo Graciani}
  \cventry
    {2007}
    {MSc in Astrophysics, Particle Physics and Cosmology}
    {Universitat de Barcelona (Spain)}
    {\emph{SPD monitoring}, supervised by Ricardo Graciani}
  \cventry
    {2002--2007}
    {Degree in Physics}
    {Universitat de Barcelona (Spain)}
    {}

\section{research activities}
I have been member of the LHCb collaboration since 2007 and I am coauthor of its 193 papers.

%Since 2012 I am the trigger liaison for the LHCb Rare Decays working group and since 2013 I am the convener of the LHCb Radiative Decays working group.

\subsection{radiative decays}
    \cventry
    {2013--2015}
    {Convener of the LHCb Radiative Decays Working Group}
    {}
    {}
    \cventry
    {2014--2015}
    {Search for the $\mathbf{B^0_s\!\to \phi\phi\gamma}$ decay}
    {}
    {Violaine Bellée, Albert Puig, Karim Trabelsi. \textit{Search for $B^0_s\!\to \phi\phi\gamma$ at LHCb}, LHCb-INT-2015-024, CERN-LHCb-INT-2015-024 (2015)}
    \cventry
    {since 2012}
    {Study of the photon polarisation with $\mathbf{B^+\!\to K^+\pi^-\pi^+\gamma}$}
    {}
    {LHCb collaboration, Aaij, R. \textit{et al.}, \textit{Observation of photon polarization in the $b \to s\gamma$ transition}, Phys. Rev. Lett. \textbf{112} (2014) $161801$}
    \cventry
    {2011--2012}
    {Study of the $\mathbf{CP}$ asymmetry in $\mathbf{B^0\!\to K^{\myast0}\gamma}$}
    {}
    {LHCb collaboration, Aaij, R. \textit{et al.}, \textit{Measurement of the ratio of branching fractions ${\cal B}(B^0\!\to K^{\myast0} \gamma) /$ ${\cal B}(B^0_s\!\to \phi \gamma)$ and the direct $CP$ asymmetry in $B^0\!\to K^{\myast0} \gamma$}, Nucl. Phys. \textbf{B867} (2013) $1$--$18$}
    \cventry
    {2011--2012}
    {Study of the ratio of branching fractions of $\mathbf{B^0\!\to K^{\myast0}\gamma}$ and $\mathbf{B^0_s\!\to \phi\gamma}$}
    {}
    {LHCb collaboration, Aaij, R. \textit{et al.}, \textit{Measurement of the ratio of branching fractions $\mathcal{B}(B^0\!\to K^{\myast0}\gamma)/$ $\mathcal{B}(B_s^0\to\phi\gamma)$}, Phys. Rev. \textbf{D85} (2012) $112013$}

\subsection{trigger}
    \cventry
    {2013--2014}
    {Review of the LHCb Run I triggers}
    {}
    {Puig, A., \textit{The LHCb trigger in 2011 and 2012}, LHCb-PUB-$2014$-$046$, CERN-LHCb-PUB-$2014$-$046$ (2014)}
    \cventry
    {since 2012}
    {Trigger liaison for the Rare Decays working group}
    {}
    {}
    \cventry
    {since 2011}
    {Design and implementation of trigger strategies for radiative $\mathbf{B}$ decays}
    {}
    {Aaij, R. \textit{et al.}, \textit{The LHCb trigger and its performance in 2011}, JINST \textbf{8} (2013) P$04022$\\
     Puig, A., \textit{The HLT$2$ Radiative Topological Lines}, LHCb-PUB-$2012$-$002$. CERN-LHCb-PUB-$2012$-$002$ (2012)}

\subsection{computing}
    \cventry
    {2012--2014}
    {Main developer and responsible for the SciFi test beam analysis software}
    {}
    {}
    \cventry
    {2011--2012}
    {Integration of the DIRAC middleware with the WS-PGRADE portal to allow the execution of gUSE workflows in a distributed computing environment}
    {}
    {Puig, A. \emph{et al.}, \textit{Integration of the gUSE/WS-PGRADE and InSilicoLab portals with DIRAC}, J. Phys. Conf. Ser. \textbf{396} (2012) $032088$}
    \cventry
    {2010}
    {Analysis of the LHCb users behavior patterns on the Grid by dumping the information from the DIRAC Accounting database}
    {}
    {Casaj{\'u}s, A. \emph{et al}, \textit{The LHCb experience on the Grid from the DIRAC accounting data}, J. Phys. Conf. Ser. \textbf{331} (2011) $072059$}
    \cventry
    {2007--2010}
    {Design and implementation of a system to perform prompt event reconstruction in the LHCb Online farm}
    {}
    {Puig, A. and Frank, M., \textit{Event reconstruction in the LHCb online cluster}, J. Phys. Conf. Ser. \textbf{219} (2010) $022020$}

\subsection{hardware r\&d}
    \cventry
    {2012--2014}
    {R\&D studies on SiPM for the LHCb Upgrade, including clustering algorithms and cosmic rays tests}
    {}
    {Bay, A. \emph{et al.}, \textit{Viability Assessment of a Scintillating Fibre Tracker for the LHCb Upgrade}, LHCb-PUB-2014-015. CERN-LHCb-PUB-2014-015. LHCb-INT-2013-004 (2014)}
    \cventry
    {2008--2011}
    {Fine calibration of the LHCb Electromagnetic Calorimeter with $\mathbf{\pi^0}$}
    {}
    {Belyaev, I. \emph{et al.}, \textit{Kali: The framework for fine calibration of the LHCb electromagnetic calorimeter}, J. Phys. Conf. Ser. \textbf{331} (2011) $032050$}
    \cventry
    {2007--2008}
    {Design and implementation of the monitoring of the LHCb SPD subdetector}
    {}
    {Abellan Beteta, C. \emph{et al.}, \textit{Time alignment of the front end electronics of the LHCb calorimeters.}, J. Instrum. \textbf{7} (2011) P$08020$}

\ifthenelse{\boolean{includeconferences}}
{
\section{conference contributions and seminars}

    \cventry
        {2015}
        {Preparation and commissioning of LHCb for Run II of LHC}
        {Isola d'Elba (Italy)}
        {Talk at \emph{13th Pisa Meeting on Advanced Detectors}, May 24--30}
    \cventry
        {2015}
        {The LHCb Turbo Stream}
        {Isola d'Elba (Italy)}
        {Poster at \emph{13th Pisa Meeting on Advanced Detectors}, May 24--30}
    \cventry
        {2014}
        {Radiative electroweak penguins at LHCb}
        {Edinburgh (United Kingdom)}
        {Talk at \emph{15th International Conference on B-Physics at Frontier Machines}, July 14--18}
    \cventry
        {2014}
        {Observation of photon polarization in the $\mathbf{b\to s\gamma}$ transition at LHCb}
        {CERN (Switzerland)}
        {\emph{LHC Seminar} on March 18th}
    \cventry
        {2013}
        {The LHCb Trigger System: Performance and Outlook}
        {Seoul (South Korea)}
        {Talk at \emph{IEEE Nuclear Science Symposium} 2013, October 27--November 2}
    \cventry
        {2013}
        {Radiative $\mathbf{B}$ decays at LHCb}
        {Stockholm (Sweden)}
        {Talk at \emph{EPSHEP} $2013$, July 18--24}
    \cventry
        {2013}
        {Rare beauty and charm decays}
        {Ann Arbor, Michigan (USA)}
        {Talk at \emph{KAON}$2013$, April 29--May 1}
    \cventry
        {2012}
        {Radiative $\mathbf{B}$ decays in LHCb}
        {Benasque (Spain)}
        {Talk at \emph{International Meeting on Fundamental Physics}, May 24--June 3}
    \cventry
        {2012}
        {Integration of the gUSE/WS-PGRADE and InSilicoLab portals with DIRAC}
        {New York (USA)}
        {Poster at \emph{Computer in High Energy and Nuclear Physics (CHEP) 2012}, May 21--25}
    \cventry
        {2012}
        {Radiative $\mathbf{B}$ decays in LHCb}
        {Marseille (France)}
        {Seminar at CPPM, March 22}
    \cventry
        {2012}
        {Results on radiative $\mathbf{B}$ decays}
        {Lake Louise (Canada)}
        {Talk at \emph{Lake Louise Winter Institute}, February 19--25}
    \cventry
        {2011}
        {Radiative $\mathbf{B}$ decays at LHCb}
        {Barcelona (Spain)}
        {Talk at \emph{III CPAN Days}, November 2--4}
    \cventry
        {2011}
        {Exclusive rare $\mathbf{B}$ decays at LHCb}
        {Durham (United Kingdom)}
        {Talk at \emph{IPPP Flavour and the 4th generation}, September 14--16}
    \cventry
        {2010}
        {The LHCb experience on the Grid from the DIRAC Accounting data}
        {Taipei (Taiwan)}
        {Poster at \emph{Computing in High Energy and Nuclear Physics (CHEP) 2010}, October 18--22}
    \cventry
        {2010}
        {Kali: the framework for fine calibration of LHCb Calorimeter}
        {Taipei (Taiwan)}
        {Poster at \emph{Computing in High Energy and Nuclear Physics (CHEP) 2010}, October 18--22}
    \cventry
        {2009}
        {Calibraci\'{o}n fina del calor\'{i}metro electromagn\'{e}tico de LHCb}
        {Ciudad Real (Spain)}
        {Talk at \emph{XXXII Reuni\'{o}n Bienal de la RSEF}, September 7--11}
    \cventry
        {2009}
        {Event reconstruction in the LHCb Online cluster}
        {Prague (Czech Republic)}
        {Talk at \emph{Computing in High Energy and Nuclear Physics (CHEP) 2009}, March 23--27}
}{}

\ifthenelse{\boolean{includeteaching}}
{
\section{teaching duties}
    \cventry
        {2014--2015}
        {MSc Thesis supervisor}
        {\epfl(Switzerland)}
        {Violaine Bellée, \emph{Search for the $B_s^0\rightarrow \phi \phi\gamma$ decay at LHCb}, Autumn Semester}
    \cventry
        {2014}
        {TP4 Project supervisor}
        {\epfl(Switzerland)}
        {Violaine Bellée, \emph{Search for the $B^0\rightarrow \phi K^{\myast0}\gamma$ and $B_s^0\rightarrow \phi \phi\gamma$ decays at LHCb}, Spring Semester}
    \cventry
        {2013--2014}
        {MSc Thesis supervisor}
        {\epfl(Switzerland)}
        {Eleonie Van Schreven, \emph{Photon polarisation sensitivity in $B^0_s\rightarrow \phi\gamma$ decays at LHCb}, Autumn Semester}
    \cventry
        {2013}
        {TP4 Project supervisor}
        {\epfl(Switzerland)}
        {Brice Maurin, \emph{Improving the selection for the decay $B^0\rightarrow K^{\myast0} \gamma$}, Spring Semester}
    \cventry
        {2012--2013}
        {MSc Thesis supervisor}
        {\epfl(Switzerland)}
        {Isaure Leboucq, \emph{Observation of the decay $B^+\rightarrow K^+\pi^-\pi^-\gamma$ at LHCb}, Autumn Semester}
    \cventry
        {2011-2012}
        {Physics lab}
        {Universitat de Barcelona (Spain)}
        {Faculty of Chemistry, Autumn Semester}
    \cventry
        {2011}
        {Taller de Altas Energ\'{i}as}
        {Universidad del País Vasco, Bilbao (Spain)}
        {Exercise supervisor for \emph{ATLAS Physics} course, under Peter Jenni (CERN).\\
         Exercise supervisor for \emph{Standard Model} course, under Nuria Rius (IFIC).}
        %{July 11--22}
    \cventry
        {2010--2011}
        {Lab fundamentals}
        {Universitat de Barcelona (Spain)}
        {Faculty of Physics, Spring Semester}
    \cventry
        {2009--2010}
        {Modern Physics Lab}
        {Universitat de Barcelona (Spain)}
        {Faculty of Physics, Autumn Semester}
}{}
    
%\section{references}
%Available upon request

%\section{computer skills}

%\section{selected publications}

%\section{LHCb papers}

\end{document}

% EOF
